% !TeX TS-program = xelatex

\documentclass[letterpaper, 11pt]{article}
\usepackage{alancv}
\usepackage{datetime2}

\begin{document}

\SetCVName{Ziyue ``Alan'' Xiang}
\SetCVJobTitle{Research Assistant}
\SetCVPhone{(+1)-510-684-2200}
\SetCVEmail{\href{mailto:xiang71@purdue.edu}{xiang71@purdue.edu}}
\SetCVOrganization{Video and Image Processing Laboratory (VIPER), \\
School of Electrical and Computer Engineering,\\
Purdue University--West Lafayette}
\SetCVLinkedin{\url{https://www.linkedin.com/in/ziyue-alan-xiang/}}
\SetCVGithub{\url{https://github.com/xziyue}}
\SetCVAddress{West Lafayette, Indiana, USA}
\SetCVLanguage{Chinese Mandarin, English, Cantonese}
\SetCVORCID{\href{https://orcid.org/0000-0001-6054-5801}{0000-0001-6054-5801}}
\SetCVGoogleScholar{\href{https://scholar.google.com/citations?user=UKO6iCgAAAAJ}{UKO6iCgAAAAJ}}
\SetCVBibSearchName{Ziyue Xiang; Xiang, Ziyue; Xiang,Ziyue}

\maketitle

\section{Education}

\begin{itemize}

\begin{itemntl}{Ph.D. in Electrical and Computer Engineering}{Aug. 2020--Present}
{Purdue University, West Lafayette, Indiana, USA}
\end{itemntl}

\begin{itemntl}{Msc. in Computer Science}{Aug. 2018--May 2020}
{Syracuse University, Syracuse, New York, USA}
\end{itemntl}

\begin{itemntl}{Berkeley International Study Program}{Aug. 2016--Dec. 2016}
{University of California, Berkeley California, USA}
\end{itemntl}

\begin{itemntl}{Bsc. in Information and Computing Science}{Sept. 2014--June 2018}
{Sun Yat-sen University, Guangdong, China}
\begin{itemize}
\item Best undergraduate thesis award
\end{itemize}
\end{itemntl}

\end{itemize}



\section{Work Experience}

\begin{itemize}

\begin{itemntl}{Research Assistant}{Aug. 2020--Present}
{\doublehref{https://engineering.purdue.edu/~ips/}{\small Video and Image Processing Laboratory (VIPER), ECE, Purdue University}}

\begin{itemize}
\item Conducting research under the \doublehref{https://engineering.purdue.edu/SEMAFOR/}{SemaFor} program
\item Investigating reliable and cost-effective approach to counter deepfake and other types of media manipulation techniques that bring substantial threat to the credibility of information
\end{itemize}
\end{itemntl}

\begin{itemntl}{Teaching Assistant}{Jan. 2020--May 2020}
{EECS, Syracuse University}

\begin{itemize}
\item Teaching assisant of \textit{CIS-375: Discrete Mathematics} lectured by Prof. Andrew C. Lee
\item Responsible for grading, hosting office hours, and preparing recitation materials
\item Researched and practiced the transition to online learning during the COVID-19 pandemic
\end{itemize}
\end{itemntl}

\begin{itemntl}{Research Assistant}{Aug. 2018--July 2020}
{\doublehref{https://scienceofscience.org/}{SOS+CD Lab, iSchool, Syracuse University}}
\begin{itemize}
\item Developed techniques to detection figure manipuluation in scientific publications
\item Assisted in a successful grant application from US Office of Research Integrity
\item Participated in the organization of the first \doublehref{https://cri-conf.org/}{Computational Research Integrity Conference}
\end{itemize}

\end{itemntl}

\end{itemize}

\section{Publication}

\CVPrintBib{ref}


\section{Online Projects}

\section{Skills}

\par\noindent\CVSkillBlock{95}{Python}~\CVSkillBlock{85}{C++}~\CVSkillBlock{75}{Cython}~\CVSkillBlock{80}{Lua}~\CVSkillBlock{80}{HTML/CSS/JavaScript}~\CVSkillBlock{98}{\LaTeX}~\CVSkillBlock{70}{Haskell}~\CVSkillBlock{70}{Julia}
\par\noindent \CVSkillBlock{80}{Data Mining}~\CVSkillBlock{85}{Data Visualization}~\CVSkillBlock{85}{Machine Learning}~\CVSkillBlock{80}{Computer Vision}~\CVSkillBlock{75}{Linux Security}~\CVSkillBlock{75}{Cybersecurity}
\par\noindent \CVSkillBlock{75}{tensorflow}~\CVSkillBlock{70}{Apache Spark}

\DTMNow

\end{document}
